### 2017-03-29 paper/oopsla17-submission/discussion.tex
some discussion

\paragraph{Additional Features}
\begin{itemize}
\item def-use chains
\item connect function and arguments in application (right now each only know about the application itself)
\item ??
\end{itemize}

\paragraph{User-Defined Types}
\begin{itemize}
\item Hard to support in general, as each data and type constructor gets
  its own set of syntactic features.
\item Attempt to mitigate by adding generic ``is-datacon'' and
  ``is-match'' feature, unclear how much it will help
\end{itemize}

\paragraph{Independent vs Joint Predictions}
We treat each sub-expression as if it exists in a vacuum, in reality
making a positive prediction for one expression may make another
prediction much less likely \citep{Raychev2015-jg}. We compensate
somewhat by ranking predictions by ``confidence'', but would be
interesting to see how structured learning would perform.

>>>>

We have shown that we can outperform the state of the art in type error
localization by learning a model of the errors that programmers make,
using a set of features that closely resemble the information the type
checker sees.
%
However, there is certainly room for improvement.
%
In this section we highlight some limitations of our approach and
potential avenues for future work.

\paragraph{User-Defined Types}
Probably the single biggest limitation of our technique is that we have
features for specific data and type constructors.
%
Anything our models learn about errors made with the |::| constructor or
the |list| type cannot easily be translated to new, user-defined
datatypes the model has never encountered.
%
We can attempt to mitigate this to some extent by adding generic
syntactic features for data constructors and match expressions, but it
remains to be seen how much these help \ES{TODO: UW data!}.
%
Furthermore, there is no obvious analog for transferring knowledge to
new type constructors, which we have seen are both more compact and
helpful.

As an alternative to encoding information about \emph{specific}
constructors, we might investigate a more abstract representation.
%
For example, instead of modeling |x :: 2| as a |::| constructor with a
right child of type |int|, we might model it as some (unknown) constructor
whose right child has an incompatible type.
%
We might symmetrically model the |2| as an integer literal whose type is
incompatible with its parent.
%
Anything we learn about |::| and |2| can now be transferred directly to
yet unseen types, but we run the risk generalizing \emph{too much} ---
\ie perhaps programmers make different mistakes with |list|s than they
do with other types, and are thus likely to choose different fixes.
%
Balancing the trade-off between specificity and generalizability appears
to be a challenging task.

% \begin{itemize}
% \item Hard to support in general, as each data and type constructor gets
%   its own set of syntactic features.
% \item Attempt to mitigate by adding generic ``is-datacon'' and
%   ``is-match'' feature, unclear how much it will help
% \end{itemize}

\paragraph{Additional Features}
There are a number of other features that could improve the model's
ability to localize errors, that would be easier to add than
user-defined types.
%
For example, each occurrence of a variable knows only its type and the
immediate context in which it occurs, but it may be helpful to know
about \emph{other} occurrences of the same variable.
%
If a variable is generally used in the context of a |float| but has a
single occurrence in the context of an |int|, it seems likely that the
latter occurrence (or context) is to blame.
%
Similarly, arguments to a function application are not aware of the
typing constraints imposed on them by the function (and vice versa),
they only know that they are occurring in the context of an application
and the type of the application itself.
%
Finally, \emph{n-grams} on the token stream have proven effective for
probabilistic modeling of programming languages, we may find that they
aid in our task as well.
%
For example, if the observed tokens in an expression diverge from the
n-gram model's predictions, that indicates that there is something
unusual about the program at that point, and it may signal an error.

% \begin{itemize}
% \item def-use chains
% \item connect function and arguments in application (right now each only know about the application itself)
% \item ??
% \end{itemize}

\paragraph{Independent vs Joint Predictions}
We treat each sub-expression as if it exists in a vacuum, but in reality
the program has a rich \emph{graphical} structure, particularly if one adds
edges connecting different occurrences of the same variable.
%
\citet{Raychev2015-jg} have used these richer models to great effect to
make \emph{interdependent} predictions about programs, \eg
de-obfuscating variable names or even inferring types.
%
One could even view our task of locating the source of an error as simply
another property to be predicted over a graphical model of the program.
%
One of the key advantages of a graphical model is that the predictions
made for one node can influence the predictions made for another node,
this is known as \emph{structured learning}.
%
For example, if, given the expression |1 + true|, we predict |true| to
be erroneous, we may be much less likely to predict |+| as erroneous.
%
We compensate somewhat for our lack of structure by ranking our
predictions by ``confidence'', but it would be interesting to see how
structured learning over graphical models would perform.
